---
title: "Data Manipulation Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(stringr)
```

Question 1.
Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

```{r}
cc_tweets <- read_csv("data/code_clan_tweets.csv")
```

```{r}
dim(cc_tweets)

names(cc_tweets)

cc_tweets
```


Question 2.
Find the total number of favourites (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}
no_favs <- cc_tweets %>% 
  filter(is_quote == F) %>% 
  summarise(sum(favorite_count))
  
```


Question 3.
Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r}
cc_tweets %>% 
  filter(is_quote == F) %>% 
  group_by(source) %>% 
  summarise(mean_retweets = mean(retweet_count))
  
```


Question 4.
Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

```{r}
total_likes <- cc_tweets %>% 
  group_by(media_type) %>% 
  summarise(sum(favorite_count)) %>% 
  mutate(media_type = coalesce(media_type, "text"))
  
```


Question 5.
Find the mean number of characters that a CodeClan tweet contains. You can either find a way to count the text in the text variable, or use the variable display_text_width which contains a count. Checking both would be a good idea if possible to see if they match (but it’s not essential).

```{r}
character_mean_using_display <- cc_tweets %>% 
  summarise(mean_char = mean(display_text_width))
character_mean_using_display
  
  
  
  
char_mean_using_strlength <- cc_tweets %>% 
   mutate(total_tweet_lenth = str_length(text)) %>% 
  summarise(mean_length = mean(total_tweet_lenth))
char_mean_using_strlength
```


Question 6.
The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}
cc_info <- read_csv("data/code_clan_info.csv")

cc_info
cc_tweets
```

```{r}
tweets_and_info <- cc_info %>% 
  left_join(cc_tweets,
            by = "tweet_id")
```


Question 7.
From your new joined data, create a new tibble codeclan_hashtags containing only tweet_id and hashtags, then convert hashtags into lowercase for analysis. Keep only those tweets with hashtags.


```{r}
codeclan_hashtags <- tweets_and_info %>% 
  select(tweet_id, hashtags) %>% 
  mutate(hashtags = str_to_lower(hashtags)) %>% 
  drop_na(hashtags)

codeclan_hashtags
```


4 Extensions


Question 8.
Some tweets have more than one hashtag, denoted by the c( symbols at the start of the string. Use the str_sub() and str_detect() functions and your codeclan_hashtags tibble from above to find all the cases in which the hashtag string begins with characters c(.

```{r}
pattern <- "c\\("

codeclan_hashtags %>%  
  mutate(multiple_tags = str_detect(hashtags, pattern)) %>% 
  filter(multiple_tags == TRUE)
codeclan_hashtags
  
## FROM ANSWERS
hashtags_multiple <- codeclan_hashtags %>% 
  mutate(first_letters = str_sub(hashtags, 1, 2)) %>%
  filter(str_detect(first_letters, "c\\("))

hashtags_multiple
```




Question 9.
Use the str_detect() function to find all tweets with text that mentions “Edinburgh”, and count how many such tweets there are.

```{r}
edin_tweets <- cc_tweets %>% 
  mutate(mentions_edin = str_detect(text, "Edinburgh")) %>% 
  summarise(mentions_edin_count = sum(mentions_edin))
edin_tweets
```



Question 10.
Use str_extract_all() with a regular expression to find out which Twitter users CodeClan have been tweeting.

```{r}
cc_messages <- cc_tweets %>% 
  mutate(who_cc_tweet = str_extract_all(text, "@[a-zA-z0-9_]+"), .after = tweet_id) %>% 
  mutate(who_cc_tweet = str_remove_all(who_cc_tweet, "@")) %>%
  mutate(who_cc_tweet = na_if(who_cc_tweet, "character(0)")) %>% 
  filter(is_retweet == FALSE) %>% 
  drop_na(who_cc_tweet)
  
cc_messages

user_pattern <- "@[a-zA-Z0-9_]+"
tweets <- cc_tweets %>% 
  pull(text) %>% 
  str_extract_all(user_pattern) %>% 
  flatten_chr() %>% 
  unique()
tweets
```
- Break it down
- Work on a subset first
- Build it up one step at a time

some chars are _meta-characters_
e.g. +*^$

These are chars that have a special meaning in a regex context

If you try to search for these the regex engine will try and use them in their __meta__ capacity

If you want to find an actual, literal meta-chat we have to _escape_

- using `\\` before the specific meta-char

```{r}
s <- "([.*hello"

pattern <- "\\(\\[\\.\\*"
```

Sometimes the _secret_formula is easier to find for getting rid of the bit you don't want, rather than the bit you do want


