---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(skimr)
```

```{r}
phone_data <- read_csv("data/20190928-items.csv")

phone_data <- phone_data %>% 
  clean_names()

phone_data %>% 
  skim()

```

Question 2.
Find the brand with the highest numbers of phones in the dataset.

```{r}
phone_data %>% 
  group_by(brand) %>% 
  summarise(total = n()) %>% 
  arrange(desc(total))
```
- Samsung has the most phones with 397

Question 3.
For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?

You will need to calculate the mean() and sd() of the ratings to plot the appropriate normal distribution. Alternatively, investigate using the fitdistr() function in the MASS package


```{r}
samsung_stats <- phone_data %>% 
  filter(brand == "Samsung") %>% 
  summarise(num = n(),
            mean = mean(rating),
            sd = sd(rating))


phone_data %>% 
  filter(brand == "Samsung") %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = after_stat(density)),
                 col = "white",
                 binwidth = 0.1
                 ) +
    stat_function(
    fun = dnorm,
    args = list(
      mean = samsung_stats$mean,
      sd = samsung_stats$sd
    ),
    col = "indianred"
  )
```

- I think the normal distribution does provide a good model for these ratings. There is a definite peak around the mean at 3.57 with most of the data fitting within the parameters of the standard deviation. 


Question 4.
We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the mean() and sd() of your distribution in an earlier question. Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.

```{r}
# proportion within 1sd
samsung_ratings <- phone_data %>% 
  filter(rating >= samsung_stats$mean - samsung_stats$sd) %>%
  filter(rating <= samsung_stats$mean + samsung_stats$sd) %>%
  summarise(prop_within_1sd = n() / nrow(samsung_ratings))

# Calculate total number 
total_ratings <- phone_data %>% 
  summarise(n()) %>% 
  pull()

# Percentage of values within 1 sd in a normal distribution
nd_1sd <- 100 * (pnorm(q = 1) - pnorm(q = -1))

# samsung prop within 1sd
samsung_prop_1sd <- 100 * (samsung_ratings$prop_within_1sd / total_ratings)

```

- This is 10% higher than you would find for a normal distribution


```{r}
samsung_ratings <- phone_data %>% 
  filter(rating >= samsung_stats$mean - (2 * samsung_stats$sd)) %>%
  filter(rating <= samsung_stats$mean + (2 * samsung_stats$sd)) %>%
  summarise(prop_within_2sd = n() / nrow(samsung_ratings))


# Calculate total number 
total_ratings <- phone_data %>% 
  summarise(n()) %>% 
  pull()

# Percentage of values within 1 sd in a normal distribution
nd_2sd <- 100 * (pnorm(q = 2) - pnorm(q = -2))

# samsung prop within 1sd
samsung_prop_2sd <- 100 * (samsung_ratings$prop_within_2sd / total_ratings)

```
- This is 2% lower than you would find for a normal distribution

```{r}
samsung_ratings <- phone_data %>% 
  filter(rating >= samsung_stats$mean - (3 * samsung_stats$sd)) %>%
  filter(rating <= samsung_stats$mean + (3 * samsung_stats$sd)) %>%
  summarise(prop_within_3sd = n() / nrow(samsung_ratings))


# Calculate total number 
total_ratings <- phone_data %>% 
  summarise(n()) %>% 
  pull()

# Percentage of values within 1 sd in a normal distribution
nd_3sd <- 100 * (pnorm(q = 3) - pnorm(q = -3))

# samsung prop within 1sd
samsung_prop_3sd <- 100 * (samsung_ratings$prop_within_3sd / total_ratings)

```
- This is 1% lower than you would find for a normal distribution. This is very close to that of a normal distribution
