---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(CodeClanData)
```

1. Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.

```{r}
names(backpack)

dim(backpack)
```

2. What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.


```{r}
backpack %>% 
  ggplot() +
  aes(x = backpack_weight) +
  geom_histogram(colour = "white") +
  labs(x = "Backpack Weight (kg)",
       y = "Count",
       title = "Distribution of Backpack Weight")
```
- This shows that the majority of backpack weights are around 10kg.


3. Are there differences in backpack weight between sex?
```{r}
backpack %>% 
  ggplot() +
  aes(x = backpack_weight, fill = sex) +
  geom_histogram(position = "dodge", binwidth = 1) +
  labs(x = "Backpack Weight (kg)",
       y = "Count",
       title = "Distribution of Backpack Weight",
       fill = "Sex")
```
- This shows that males carry slightly heavier backpacks than females.

4. What is the relationship between body weight and backpack weight?

```{r}
backpack %>% 
  ggplot() +
  aes(x = body_weight, y = backpack_weight) +
  geom_point() +
  geom_smooth(method = lm,
              se = FALSE) +
  labs(x = "Body Weight",
       y = "Backpack Weight",
       title = "Relationship between Backpack and Body Weight")
                    
```
- This scatter plot shows a correlation between body weight and backpack weight.

5. Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}
backpack %>% 
  ggplot() +
  aes(x = body_weight, y = backpack_weight) +
  geom_point() +
  geom_smooth(method = lm,
              se = FALSE) +
  facet_wrap(~ sex) +
  labs(x = "Body Weight",
       y = "Backpack Weight",
       title = "Relationship Between Backpack and Body Weight")
```
- Initially these plots show that there is a stronger correlation between body weight and backpack weight in females than in males. But if I change the limits to show the majority of people from each sex, with no extremes, it shows a very similar correlation. Meaning that the `sex` doesn't matter too much, it's more the `body_weight`. 

```{r}
backpack %>% 
  ggplot() +
  aes(x = body_weight, y = backpack_weight) +
  geom_point() +
  geom_smooth(method = lm,
              se = FALSE) +
  facet_wrap(~ sex) +
    scale_y_continuous(expand = c(0,0),
                     limits = c(0, 30)) +
  scale_x_continuous(limits = c(100, 200)) +
  labs(x = "Body Weight",
       y = "Backpack Weight",
       title = "Relationship Between Backpack and Body Weight")
```

6. What proportion of students report back pain?
```{r}
back_pain_prop <- backpack %>% 
  summarise(back_p_prop = sum(back_problems) / n())
back_pain_prop

back_pain <- backpack %>% 
  mutate(back_problems = case_when(
    back_problems == 1 ~ "Yes",
    back_problems == 0 ~ "No"))

back_pain %>% 
  ggplot() +
  aes(x = back_problems) +
  geom_bar() +
  labs(x = "Back Problems",
       y = "Count",
       fill = NULL)
```

- This shows that around 1/3 of students reported back pain


7. Is this proportion different between men and women?
```{r}
back_pain <- backpack %>% 
  mutate(back_problems = case_when(
    back_problems == 1 ~ "Yes",
    back_problems == 0 ~ "No"))
    
back_pain %>% 
  ggplot() +
  aes(x = back_problems, fill = sex) +
  geom_bar(position = "fill") +
  labs(x = "Back Problems",
       y = "Count",
       title = "Proportion of Students with Back Problems",
       fill = NULL)

```
- This shows that a higher proportion of females have reported back problems.

8. Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

```{r}
back_pain %>% 
  ggplot() +
  aes(x = body_weight, y = backpack_weight, colour = sex) +
  geom_point() +
  facet_wrap( ~ back_problems) +
  labs(x = "Body Weight",
       y = "Backpack Weight",
       fill = NULL,
       title = "Relationship Between Backpack Weight and Body Weight")
```

- This shows that the majority of people reporting back pain are females in the 100 - 150kg weight range.
