---
title: "Week 1 Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(skimr)
#library(lubridate)
```

```{r}
books <- read_csv("data/books.csv")
```

## Explore the data
```{r}
view(books)

dim(books)

# Useful info such as number of missing values and quartiles
skim(books)

names(books)

glimpse(books)

# Top 10 books with higest average rating
# Problem discovered where books have 1 or very few reviews 
books %>% 
slice_max(average_rating,n = 10)

# Tells me the data type of each variable/column
sapply(books, class)

```

## Clean up the data

```{r}
books_clean <- books %>% 
  clean_names() %>% 
  rename("row_id" = "rowid",
         "isbn_13" = "isbn13"
         )
books_clean

# If I need to change the type of variable
# books_clean %>%
#   mutate(average_rating = as.numeric(average_rating))
```


## Find any missing values

```{r}
# Finds the total sum of NA values in books
sum(is.na(books_clean))

# Counts the number of NA values - returns TRUE or FALSE
table(is.na(books_clean))

books_clean %>% 
  filter(num_pages == "0")
```
- Did not discover any missing values. There are a lot of "0"s in there where there shouldn't be (e.g. you can't have 0 page numbers).

- I've decided to basically not do anything with them. I don't think removing them would be appropriate due to them having missing info. 

- Obviously they won't be included in some findings if they have 0 reviews or pages, but I don't think manufacturing an average_rating would be fair.

### The best (and worst) books with the highest ratings where the rating count is over a certain number
# and Remove J.K. Rowling
```{r}

# Using quantile to calculate a value to use as the ratings_count must be above a certain number. 
quartiles <- unname(
  quantile(books_clean$ratings_count))

low_quart <- quartiles[2]

best_books <- books_clean %>% 
  filter(authors != "J.K. Rowling" 
         & authors != "J.K. Rowling/Mary GrandPré"
         & ratings_count > low_quart) %>% 
  select(title, 
         authors,
         average_rating) %>% 
  slice_max(average_rating, n = 5)
best_books

worst_books <- books_clean %>% 
  filter(ratings_count > low_quart) %>% 
  select(title, 
         authors, 
         average_rating) %>% 
  slice_min(average_rating, 
            n = 5)
worst_books
```

## The publishers with the highest number of ratings + text reviews

```{r}
pub_most_reviews <- books %>% 
  select(publisher,
         ratings_count,
         text_reviews_count) %>% 
  group_by(publisher) %>% 
  summarise(ratings_reviews_total =
              sum(ratings_count) + 
              sum(text_reviews_count)) %>%
  arrange(desc(ratings_reviews_total))
pub_most_reviews
```

## Add a new column giving the book a character vector called "book_quality", rating it excellent, good, okay, poor or terrible.

```{r}
# Filter using the low quart to deal with books who either have none or very few ratings - making their averages very low or high.

books_clean <- books_clean %>% 
  filter(ratings_count > low_quart) %>% 
  mutate(book_quality = case_when(
    average_rating <= 1 ~ "Terrible",
    average_rating <= 2 ~ "Poor",
    average_rating <= 3 ~ "Okay",
    average_rating <= 4 ~ "Good",
    average_rating <= 5 ~ "Excellent"
  ))
books_clean
  
```

## Using the quartiles of the average_rating to update the column, give them a new rating of book_quality
```{r}

avg_rate_quart <- unname(
  quantile(books_clean$average_rating))

books_clean_update <- books_clean %>% 
  filter(ratings_count > low_quart) %>% 
  mutate(book_quality = case_when(
    average_rating == 0 ~ "No Rating",
    average_rating <= avg_rate_quart[1] ~ "Terrible",
    average_rating <= avg_rate_quart[2] ~ "Poor",
    average_rating <= avg_rate_quart[3] ~ "Okay",
    average_rating <= avg_rate_quart[4] ~ "Good",
    average_rating <= avg_rate_quart[5] ~ "Very Good",
    average_rating <= 5 ~ "Amazing"
  )) 
books_clean_update
```

## The 10 oldest books where book_quality == "Very Good" or "Amazing"

```{r}

top_old_books <- books_quality %>% 
  select(title,
         book_quality,
         publication_date) %>% 
  filter(book_quality == "Very Good"
         | book_quality == "Amazing") %>% 
  arrange(publication_date) %>% 
  head(10)
top_old_books
```


## The top 5 authors who have released 10 or more books.

```{r}
# Group the authors. Count the number of books they have released. Calculate the mean of the average_rating of each of the authors books and round to 2 decimal places.

top_author <- books_clean_update %>% 
  group_by(authors) %>% 
  summarise(book_count = n(),
            overall_avg = round(mean((average_rating)), 2)
  ) %>%
  filter(book_count >= 10) %>% 
  arrange(desc(overall_avg)) %>% 
  head(5)
top_author

# A problem I discovered is that this only works when the authors name has been input exactly/correctly. This also does not calculate the sum of books written if an author has written books on their own but also collaborated.
```