---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(gtools)
```

```{r}
titanic_deaths <- read_csv("data/titanic.csv")
source("prob.R")
```

```{r}
passenger_list <- c("1st", "2nd", "3rd")

titanic_deaths_passenger <- titanic_deaths %>% 
  mutate(passenger = case_when(
    class %in% passenger_list ~ TRUE,
    TRUE ~ FALSE
  ))

titanic_deaths_passenger %>% 
  filter(passenger == TRUE)
```

Q. prob(survived∣crew) and prob(survived∣passenger) 

```{r}

cont_table <- titanic_deaths_passenger %>% 
  tabyl(survived, passenger)


prob_table <- cont_table %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all")

```
Prob(survived | crew) = p(survived AND crew) / p(crew)
                      = 0.0956 / 0.403
```{r}
# Prob(survived | crew) = p(survived AND crew) / p(crew)
#                       = 0.0956 / 0.403
0.0956 / 0.403
```
```{r}
# Prob(survived | passenger) = p(survived AND passenger) / p(passenger)

0.227 / 0.597

```
- This shows there was a higher probability you would survive if you were a passenger

Question 1.
If I roll a six-sided dice once, what is the probability of getting a number less than 5?

p(<5) = 4/6 = 2/3

Question 2.
How many outcomes are there in the sample space of an experiment in which we toss three dice?

```{r}
s_three_dice <- rolldie(3)

s_three_dice %>% 
  summarise(size_of_s = n())

```

Question 4.
Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

```{r}
class <- c("Karen", "Ellen","Euan", "Kasha", "Struan")

height_order <- as_tibble(permutations(n = 5, 
                                       r = 5, 
                                       v = class, 
                                       repeats.allowed = FALSE ))

prob_order <- height_order %>% 
  summarise(prob_height_order = (1 / nrow(height_order)))
```
- The probability that they sit in one exact order is 0.008


Question 6.
If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades?

```{r}
card_deck <- cards()

black_cards <- c("Club", "Spade")

card_deck_black_card <- card_deck %>% 
  mutate(black = case_when(
    suit %in% black_cards ~ TRUE,
    TRUE ~ FALSE
  ))
#p(black | spade) = p(spade AND black) / p(spade)

p_black_spade <- card_deck_black_card %>% 
  filter(black == TRUE,
         suit == "Spade") %>% 
  summarise(p = n()/nrow(card_deck_black_card)) %>% 
  pull()

p_black <- card_deck_black_card %>% 
  filter(black == TRUE) %>% 
  summarise(p = n()/nrow(card_deck_black_card)) %>% 
  pull()

p_spade_given_black <- p_black_spade / p_black
```
- The probability of picking a spade GIVEN black is 0.5
                      

```{r}

# roll_six <- rolldie(6) %>% 
#   nrow()

# order <- c("6", "5", "4", "3", "2", "1")
# 
roll_6_factorial <- as_tibble(combinations(n = roll_six,
                                           r = 6,
                                           # v = order,
                                           repeats.allowed = FALSE))


```

```{r}
roll_six_order <- isin(roll_six, 6, ordered = FALSE)
```

