---
title: "CI homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(infer)
```

```{r}
ames_data <- read_csv("data/ames.csv") %>% 
  clean_names()
```
```{r}
ames_data %>% 
  ggplot(aes(x = lot_area)) +
  geom_histogram(bins = 500)
```

- This is roughly a normal distribution with a few outliers


3. Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.
```{r}
infer_resample_ames <- ames_data %>%
  specify(response = lot_area) %>%
  generate(reps = 5000, type = "bootstrap") %>%
  calculate(stat = "mean")
  
  
infer_resample_ames %>% 
  ggplot(aes(x = stat)) +
  geom_histogram(colour = "white")
```

4. Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution

```{r}
infer_ci_95_ames <- infer_resample_ames %>%
  get_confidence_interval(level = 0.95,
                          type = "percentile")

mean_infer_ames <- infer_resample_ames %>%
  summarise(mean = mean(stat))

infer_resample_ames %>%
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_95_ames)
```

5. You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense?

```{r}
ci_99_ames <- infer_resample_ames %>% 
  summarise(
    mean = mean(stat),
    lower_bound = quantile(stat, probs = 0.005),
    upper_bound = quantile(stat, probs = 0.995)
    )

infer_ci_99_ames <- infer_resample_ames %>%
  get_confidence_interval(level = 0.99,
                          type = "percentile")

infer_resample_ames %>%
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_99_ames)
```
- The 99% confidence interval is slightly wider which is what we would expect [9808, 10534] compared to the 95% CI which was between [9883, 10440]

6. Calculate the point estimate of the mean(lot_area)
```{r}
mean_infer_ames <- infer_resample_ames %>%
  summarise(mean = mean(stat))
```

Ext. 1

Calculate a point estimate and 95% CI for the proportion of houses in the data built before 1920. Does the number of reps you use matter? [Investigate reps from 200 up to 50000, memory of your laptop permitting].


```{r}
pre_1920 <- ames_data %>% 
  mutate(built_pre_1920 = year_built < 1920)

# To use a numeric value instead of a logical

# ames_before_1920 <- ames_data %>%
#   mutate(before_1920 = as.numeric(year_built < 1920)) %>% 
#   select(before_1920)

bootstrap_resample_pre1920 <- pre_1920 %>% 
  specify(response = built_pre_1920, 
          success = "TRUE") %>% 
  generate(reps = 50000, type = "bootstrap") %>% 
  calculate(stat = "prop")
bootstrap_resample_pre1920


infer_ci_95_pre_1920 <- bootstrap_resample_pre1920 %>% 
  get_confidence_interval(level = 0.95,
                          type = "percentile")

bootstrap_resample_pre1920 %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_95_pre_1920)

mean_bootstrap_pre_1920 <- bootstrap_resample_pre1920 %>% 
  summarise(mean = mean(stat))
```

```{r}
bootstrap_resample_pre1920_200r <- pre_1920 %>% 
  specify(response = built_pre_1920, 
          success = "TRUE") %>% 
  generate(reps = 200, type = "bootstrap") %>% 
  calculate(stat = "prop")
bootstrap_resample_pre1920_200r

infer_ci_95_pre_1920_200r <- bootstrap_resample_pre1920_200r %>% 
  get_confidence_interval(level = 0.95,
                          type = "percentile")

bootstrap_resample_pre1920_200r %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_95_pre_1920_200r)

mean_bootstrap_pre_1920_200r <- bootstrap_resample_pre1920_200r %>% 
  summarise(point_est = mean(stat))
```

```{r}
ci_diff <- infer_ci_95_pre_1920 - infer_ci_95_pre_1920_200r
```

- There seems to be almost no difference in the lower and upper CI if you run 200 reps compared to 5000 reps. It broadens slightly towards the upper CI, possibly due to the outliers affecting the results.
